### 2018-03-21 paper/sexSelectionSpacing-ver1.tex
Future research for conclusion

First, did the spacing after girls increase relative to the spacing
after boys?
The underlying hypothese is that in the absence of sex selection son 
preference leads to shorter spacing after the birth of a girl than after the 
birth of a boy, whereas son preference increases the spacing after the birth 
of a girl relative to after the birth of a boy when prenatal sex selection is 
used.
We would still expect parents to \emph{try} to conceive earlier after the birth 
of a girl than after a boy, but the abortions will increase the 
length of the space, and may even lead to longer spacing after the
birth of girls than after boys.
[TK something on general changes in spacing? Or hold off until discussing the
results]

Second, do the shapes of survival curves differ across sex compositions 
within a spell?
The shapes of the survival curves provides clues to whether parents are
still trying to conceive earlier after girls than boys.
I expect this to be the case if there is still a strong preference for
boys, and, as discussed above, this behavior may even become more pronounced
with access to sex selection.
At a more technical level, the shapes of the survival curve serve as an
indicator for the presence of non-proportionality.

@@

\subsection{Distribution of Spacing Across Sex Compositions and Time}

@@

In the interest of space, I discuss only a representative subset.
Figure \ref{fig:pps_spell1} shows spacing within the first spell across the
four periods for rural women with no education and for urban women with 
eight or more years of education.
Figures \ref{fig:pps_low} and \ref{fig:pps_high} show spacing across sex
compositions for the second, third, and fourth spells for the first period, 
1972--1984, and the last period, 2005--2016, for rural women with no 
education and urban women with eight or more years of education.
Standard and conditional survival curves for all groups and time periods 
are shown in the Appendix, and I discuss some examples of standard survival
curves in the following section.

@@

@@

\appendix
\section{Descriptive Statistics}

@@

>>>>

First, did the spacing after girls increase relative to the spacing
after boys?
The underlying hypothesis is that in the absence of sex selection son 
preference leads to shorter spacing after the birth of a girl than after the 
birth of a boy, whereas son preference increases the spacing after the birth 
of a girl relative to after the birth of a boy when prenatal sex selection is 
available.
I still expect parents to \emph{try} to conceive earlier after the birth 
of a girl than after a boy, but the abortions will increase the 
length of the space, and may even lead to longer spacing after the
birth of girls than after boys.
[TK something on general changes in spacing? Or hold off until discussing the
results]

Second, do the shapes of survival curves differ across sex compositions 
within a spell?
The shapes of the survival curves provides clues to whether parents are
still trying to conceive earlier after girls than boys.
I expect this to be the case if there is still a strong preference for
boys, and, as discussed above, this behavior may even become more pronounced
with access to sex selection.
At a technical level, the shapes of the survival curve serve as an
indicator for the presence of non-proportionality.

@@

\subsection{Distribution of Birth Spacing Across Sex Compositions and Time}

@@

In the interest of brevity, I discuss only a representative subset.
Figure \ref{fig:pps_spell1} shows spacing within the first spell across the
four periods for rural women with no education and for urban women with 
eight or more years of education.
Figures \ref{fig:pps_low} and \ref{fig:pps_high} show spacing across sex
compositions for the second, third, and fourth spells for the first period, 
1972--1984, and the last period, 2005--2016, for rural women with no 
education and urban women with eight or more years of education.
Standard and conditional survival curves for all groups and time periods 
are shown in the Appendix, and I discuss some examples of standard survival
curves in the following section.

@@

The reversal have some weird side effects.
Because there is now longer spacing after girls and this is when
we should observe sex selection we can get an less unequal 
sex ratio in the survey data than what we will eventually observe.

This points to two important questions for future research:
What is the role of falling fertility in the use of sex selection
and is the use of sex selection increasing or decreasing over time?
[more on how to analyze those]

The results here lead to a host of larger important questions that
needs to be addressed.

First, to what extent are the improvements in health for girls
relative to boys the result of selection, longer spacing between
births, or changing son preference?

Second,

This suggestion that an overlooked approach to addressing a biased
sex ratio may be to encourage higher female labor force participation.
In addition to the obvious benefit to the women in terms of 
bargaining power, it also increases the cost of repeated 
sex-selective abortions.
[Caveat, it also lowers fertility, and everything else equal that
would may lead to higher use of sex selection]

[Stuff to add somewhere in the paper]

@@

\appendix

@@

\section{Descriptive Statistics}
\setcounter{figure}{0}
\setcounter{table}{0}
